### 2025-05-27 Manuscript/Manuscript.tex
Writthing

In relation to Postulate I, it is often convenient to represent quantum states using the \emph{density matrix} formalism, where the state is described by $\rho = \ket{\psi}\bra{\psi}$ instead of $\ket{\psi}$. In this formalism, the global phase ambiguity disappears, since if $\ket{\psi'} = e^{i\theta}\ket{\psi}$, then
\begin{align*}
	\rho' = \ket{\psi'}\bra{\psi'} = \ket{\psi}\bra{\psi} = \rho.
\end{align*}

@@

Note the constraints $\sum_{i=1}^n \Pi_i = \mathds{1}$ and $\Pi_i \geq 0$ ensure that the $\Pi_i$ form a valid POVM, since they demand positive semi-definition and form a complete measurement. The superscript $e$ in $P_{\text{\gls{me}}}^e$ indicates that this is the \emph{error probability}.

@@

Naturally, both formulations are related via:
\begin{align*}
P_{\text{\gls{me}}}^s + P_{\text{\gls{me}}}^e = 1.
\end{align*}

In the case of the \gls{ze} protocol, the POVMs must also satisfy an unambiguity condition, i.e. each measurement operator $\Pi_i$ must be orthogonal to the corresponding state $\rho_i$. In other words,
\begin{align*}
\tr(\Pi_i \rho_i) = 0 \quad \forall i \in \{1, \dots, n\}.
\end{align*}

To ensure completeness, we introduce an additional POVM element $\Pi_?$ representing an inconclusive result,
\begin{align*}
\Pi_? = \mathds{1} - \sum_{i=1}^n \Pi_i.
\end{align*}
If the measurement yields the outcome $\Pi_?$ (i.e., the "?" symbol), the result is inconclusive.

@@

Let us fix an arbitrary orthonormal basis $\{\ket{\omega_i}\}_{i=1}^n$. Then, the diagonal entries of $X$ in this basis are given by,
\begin{align*}
	X_{i,i} = \braket{\omega_i|\psi_i}.
\end{align*}
\footnote{Note that fixing the basis $\{\ket{\omega_i}\}_{i=1}^n$ uniquely determines the decomposition $\mathcal{G} = X^\dagger X$, and vice versa.}We define the POVM elements as projectors $\Pi_i = \ket{\omega_i}\bra{\omega_i}$. Then, for the ensemble $\{(\rho_i, \eta_i)\}_{i=1}^n$, the corresponding semidefinite program (\gls{sdp}) constraints become,
\begin{align*}
	\tr(\Pi_i \rho_i) &= \tr\left( \ket{\omega_i}\bra{\omega_i} \ket{\psi_i}\bra{\psi_i} \right) \\
	&= |\braket{\omega_i|\psi_i}|^2 \\
	&= |X_{i,i}|^2.
\end{align*}

@@

Given a quantum state $\ket{\psi}$, referred to as the \emph{seed state}, we define a \emph{group generated ensemble} as the set of states obtained by applying a group of unitary transformations to $\ket{\psi}$. Specifically, if the ensemble consists of $n$ quantum states, its elements are of the form
\begin{align*}
	U_i\ket{\psi}, \quad i \in \{1, \dots, n\},
\end{align*}
where the set of unitary matrices $\{U_i\}_{i=1}^n$ forms a finite group under standard matrix multiplication. In terms of density matrices, the ensemble can equivalently be written as,
\begin{align*}
	\rho_i = U_i \rho U_i^\dagger, \quad i \in \{1, \dots, n\},
\end{align*}
where $\rho = \ket{\psi}\bra{\psi}$ is the density matrix corresponding to the seed state.

@@

\emph{Example: The $\mathbb{Z}/n\mathbb{Z}$ group-generated ensemble}: Let $\mathcal{U} \in U(n)$ be an $n \times n$ unitary matrix satisfying $\mathcal{U}^n = \mathds{1}$, and let $\ket{\psi}$ be the seed state. The Gram matrix $\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}}$ elements associated with the ensemble $\left\{\mathcal{U}^i\ket{\psi}\right\}_{i=0}^{n-1}$ are
\begin{align*}
	\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}}_{i,j} = \braket{\mathcal{U}^i\psi | \mathcal{U}^j\psi} = \braket{\psi | \mathcal{U}^{j-i} | \psi} = \braket{\mathcal{U}^{j-i}}_{\psi},
\end{align*}
where we use the shorthand notation,
\begin{align*}
	\braket{\mathcal{U}^k}_\psi := \braket{\psi | \mathcal{U}^k | \psi}.
\end{align*}

@@

We now identify $S_3$ as a group of unitary matrices\footnote{We treat each group element as a unitary matrix, and the group operation as matrix multiplication.}. It follows that the Gram matrix of the $S_3$ group-generated ensemble is the matrix of expected values of the Cayley table entries with respect to the seed state $\ket{\psi}$. That is,
\begin{align*}
	\mathcal{G}^{S_3}_{\psi} = \begin{pmatrix}
        1 & \braket{s}_\psi & \braket{s^2}_\psi & \braket{p}_\psi & \braket{q}_\psi & \braket{r}_\psi \\ 
        \braket{s^2}_\psi & 1 & \braket{s}_\psi & \braket{r}_\psi & \braket{p}_\psi & \braket{q}_\psi \\
        \braket{s}_\psi & \braket{s^2}_\psi & 1 & \braket{q}_\psi & \braket{r}_\psi & \braket{p}_\psi \\
        \braket{p}_\psi & \braket{r}_\psi & \braket{q}_\psi & 1 & \braket{s^2}_\psi & \braket{s}_\psi \\
        \braket{q}_\psi & \braket{p}_\psi & \braket{r}_\psi & \braket{s}_\psi & 1 & \braket{s^2}_\psi \\
        \braket{r}_\psi & \braket{q}_\psi & \braket{p}_\psi & \braket{s^2}_\psi & \braket{s}_\psi & 1
	\end{pmatrix}.
\end{align*}
Note that $\braket{e}_\psi = 1$ since $e = \mathds{1}$. Moreover, since $\mathcal{G}^{S_3}$ is Hermitian, we conclude:
\begin{align*}
\braket{p}_{\psi},\ \braket{q}_{\psi},\ \braket{r}_{\psi} \in \mathbb{R}, \quad \forall \ket{\psi} \in \mathcal{H},
\end{align*}
which implies the unitary matrices corresponding to the triangle symmetries $p$, $q$, and $r$ are Hermitian. As a matter of fact we know the eigenvalues of this matrices can only be $\pm 1$ and at least one of them must be $-1$.\footnote{Otherwise, they would be the identity and we know them to be different by construction.} This procedure generalizes to any finite group $G$, showing that computing the Cayley table is equivalent to computing the Gram matrix of the corresponding group-generated ensemble.

Finally, we denote the cardinality of a finite group $G$ (i.e., the number of its elements) as $|G|$. In scenarios with uniform prior probabilities, this implies,
\begin{align*}
	\eta_i = \frac{1}{|G|}\quad \forall i\in\{1,...,n\}.
\end{align*}
\subsection{Dual Formulation of the Problem}

@@

Significant progress has been made in the study of the state exclusion task for group-generated ensembles. In particular, the work \emph{Quantum State Exclusion for Group-Generated Ensembles of Pure States}\cite{MainPaper} presents exact analytical expressions for the success and error probabilities under both the Minimum Error \gls{me} and Zero Error \gls{ze} exclusion protocols.

Let $\mathcal{G}^G$ denote the Gram matrix of a group-generated ensemble $\left\{ \left( \rho_i, \frac{1}{|G|} \right) \right\}_{i=1}^{|G|}$, where $G$ is a finite group of size $|G|$, and let $\{\lambda_i\}_{i=1}^{|G|}$ be the set of eigenvalues of $\mathcal{G}^G$. Assume the eigenvalues are ordered increasingly,
\begin{align*}
	i \leq j \quad \Leftrightarrow \quad \lambda_i \leq \lambda_j, \quad \forall i,j \in \{1, \dots, |G|\},
\end{align*}
i.e., $\lambda_1$ is the smallest and $\lambda_{|G|}$ the largest eigenvalue.

@@

A key feature of these results is their independence from the specific group generating the ensemble. That is, for any two group-generated ensembles $A$ and $B$ corresponding to groups $G_A$ and $G_B$ (with $G_A \neq G_B$ but $|G_A| = |G_B|$), if their respective Gram matrices $\mathcal{G}^{G_A}$ and $\mathcal{G}^{G_B}$ share the same eigenvalues, then the exclusion probabilities for both \gls{me} and \gls{ze} protocols are identical. This group-independence property is a cornerstone of the present study.

@@

Let us study the Gram matrix of a limit ensemble composed of $n$ identical quantum states (i.e., the same state is repeated $n$ times in the ensemble).\footnote{This case may appear paradoxical, since there is no way to distinguish between identical states. Nevertheless, we present it as a limiting scenario.} The Gram matrix reads:
\begin{align*}
	\mathcal{G}^{\text{limit}} = \begin{pmatrix}
 1 & 1 & \cdots & 1 \\
 1 & 1 & \cdots & 1 \\
 \vdots & \vdots & \ddots & \vdots \\
 1 & 1 & \cdots & 1 \\
\end{pmatrix}.
\end{align*}

@@

Under these conditions, both \gls{qse} and \gls{qsd} are trivial, as the states form an orthonormal basis. In particular, in the space spanned by these states, we have,
\begin{align*}
	\sum_{i=1}^{n} \rho_i = \mathds{1},
\end{align*}
which means that the set $\{\rho_i\}$ is itself a \gls{povm}. The measurement corresponding to this \gls{povm} allows perfect identification (or exclusion), hence both \gls{qse} and \gls{qsd} can be performed without error.

@@

In the non-perfect exclusion regime, the analytical results for group-generated ensembles provide lower bounds on the success probabilities (and upper bounds on the error probabilities) for general ensembles.

Consider, for example, the case of an ensemble of 4 quantum states. There are exactly two groups of four elements: $\mathbb{Z}/4\mathbb{Z}$ and $\mathbb{Z}/2\mathbb{Z} \times \mathbb{Z}/2\mathbb{Z}$.\footnote{These are the only non-isomorphic groups of order 4.} This implies that there exist two specific unitary matrices, $U_{\mathbb{Z}/4\mathbb{Z}}$ and $U_{\mathbb{Z}/2\mathbb{Z} \times \mathbb{Z}/2\mathbb{Z}}$ (up to permutation of rows and columns), for which the analytical solution holds exactly.

Since $U(n)$ is compact, and assuming continuity of the exclusion probabilities with respect to $U$ under a given matrix norm, for each of these unitary matrices there exist arbitrarily small neighborhoods $\mathcal{B}(U_{\mathbb{Z}/4\mathbb{Z}})$ and $\mathcal{B}(U_{\mathbb{Z}/2\mathbb{Z} \times \mathbb{Z}/2\mathbb{Z}})$ such that the exclusion probabilities within these neighborhoods approximate the analytical result as closely as desired. However, the existence of multiple such matrices (and intersecting neighborhoods) can complicate numerical optimization and analysis.

In contrast, it is usefull to consider the case where the ensemble contains a prime number $p$ of states. In this scenario, the situation simplifies considerably, since there exists only one group (up to isomorphism) of order $p$, namely $\mathbb{Z}/p\mathbb{Z}$.

This result follows immediately from Lagrange's theorem. The theorem guarantees that the order of any element in a finite group\footnote{The order of an element $\tau$ in a group $G$ is the smallest positive integer $m$ such that $\tau^m = e$, where $e$ denotes the identity/neutral element of the group.} must divide the order of the group. Since $p$ is a prime number, the only positive integers dividing $p$ are either $1$ or $p$ itself. Therefore, the order of any group element must be either $1$ or $p$. An element of order $1$ must be the identity, so every non-identity element in the group must have order $p$. This implies that all non-identity elements generate the entire group, i.e., the group is cyclic. As a result, any group of prime order $p$ is necessarily cyclic and isomorphic to $\mathbb{Z}/p\mathbb{Z}$.

@@

Ensembles of prime cardinality are thus of particular interest and will be further explored in the Results and Discussion section. \textcolor{blue}{Add reference to Results section}
\section{Methodology}

@@

\section{Results and Discussion}

@@

The colorless regions correspond to parameters where $\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}$ is not positive semi-definite, and leading up yo non-valid Gram matrices, since positive semi-definition is inherent to a Gram matrix.

@@

Both limiting behaviors remain valid. However, the \gls{ze} success probabilities are lower than those of the \gls{me} protocol. This is explained by the stricter constraints imposed in the \gls{ze} scenario, where $\tr(\Pi_i\rho_i) = 0$ is enforced for all POVM elements except one. Notice both probabilities are computed in a completely symmetric way,
\begin{align*}
	P^s_{\gls{me}}\sim P^s_{\gls{ze}}\sim 1-\sum_{\gls{povm}}\tr{(\Pi_i\rho_i)}.
\end{align*}

Nevertheless, in the \gls{ze} case we enforce $\tr{(\Pi_i\rho_i)}=0$ for all the \glspl{povm} except one. Thus, the system is more constrained in the \gls{ze} protocol, then the optimization of the probability cannot be performed up to the same point as in the \gls{me} protocol. Hence, the success probabilities for \gls{me} are greater than the ones obtained with the \gls{ze} protocol.

@@

Notice the missing eigenvalue is determined by the other two via,
\begin{align*}
	\lambda_3=3-\lambda_1-\lambda_2.
\end{align*}
Since the Gram matrix is a positive semidefinite matrix we know that $\lambda_3\geq0$, the limit case scenario $\lambda_3=0$ defines the line,
\begin{align*}
\lambda_2=3-\lambda_1,
\end{align*}
that constraints the possible eigenvalues to only reach values under this line. Otherwise the remaining value would be negative leading up to non-valid Gram matrices as discussed in the previos plots. Naturally, we also know $\lambda_1,\lambda_2>0$, then the region $\Omega$ where the system leads up to consistent Gram matrices is,
\begin{align*}
	\Omega=\left\{(\lambda_1,\lambda_2)\in\mathbb{R}^2\left|\lambda_1\geq0,\lambda_2\geq0,\lambda_1+\lambda_2\leq3\right.\right\}.
\end{align*}
This region $\Omega$ is depicted in the Figure (\ref{FigureQSEMEZ3ZEigenValues}) as boottom left triangle, where our system is recluded. Inside this region we can find the perfect exclusion zone, i.e. the eigenvalues such that Eq.(\ref{equationPerfectExclusionCondition}) is fulfilled. In particular,if we set $\lambda_i$ with $i\in\{1,2,3\}$ to be the greatest eigenvalues and denote $\lambda_j,\lambda_k$ as the remaining 2 eigenvalues, we know perfect exclusion to be archived if,
\begin{align*}
	\sqrt{\lambda_i}\leq \sqrt{\lambda_j}+\sqrt{\lambda_k}.
\end{align*}
With a little bit of algebra and recalling that $\lambda_3=3-\lambda_1-\lambda_2$ we can derive the regime of perfect exclusion denoted as $\Delta$ comprehends the eigenvalues such that,
\begin{align*}
	(\lambda_1,\lambda_2&)\in \Delta\\
	\Updownarrow& \\
	4\lambda_1^2 + 4\lambda_2^2 + 4\lambda_1\lambda_2 - &12\lambda_1 - 12\lambda_i + 9 \leq 0
\end{align*}
Figure (\ref{FigurePerfectExclusionZ3Z}) shows the $\Delta$ region. It is inmediate that this region corresponds to the colorless perfect exclusion regime in Figure (\ref{FigureQSEMEZ3ZEigenValues}).
\begin{figure}[H]
	\centering
	\begin{overpic}[width=0.5\textwidth, trim={1.8cm 0.8cm 2cm 2cm}, clip]{GeneralSources/PerfectExclusionZoneZ3Z.pdf}
	\end{overpic}
	\caption{Plot of the $\Delta$ region.}
	\label{FigurePerfectExclusionZ3Z}
\end{figure}

@@

To illustrate this more concretely, consider the following ensamble involving qubit states,
\[
\{\ket{\textcolor{red}{\uparrow}}, \ket{\textcolor{blue}{\uparrow}}, \ket{\textcolor{green}{\uparrow}}\}.
\]
These are represented on a Bloch circle\footnote{The Bloch circle is a projection of the Bloch sphere onto a plane.} in Figure~\ref{FigureIntuitionExample}.

@@

It is evident that $\ket{\textcolor{red}{\uparrow}}$ is noticeably different from the other two states. The red arrow points in the opposite direction to the blue and green arrows. Therefore, given an unknown state $\ket{\uparrow}$ from this ensemble, it is relatively easy to determine whether $\ket{\uparrow} = \ket{\textcolor{red}{\uparrow}}$ or $\ket{\uparrow} \neq \ket{\textcolor{red}{\uparrow}}$. If $\ket{\uparrow} = \ket{\textcolor{red}{\uparrow}}$, we can exclude either $\ket{\textcolor{blue}{\uparrow}}$ or $\ket{\textcolor{green}{\uparrow}}$; otherwise, we can exclude $\ket{\textcolor{red}{\uparrow}}$. In both cases, the exclusion is straightforward.

@@

This configuration exhibits perfect symmetry. Define a unitary operator $\mathcal{U}$ such that:
\[
\mathcal{U} \ket{\textcolor{red}{\uparrow}} = \ket{\textcolor{blue}{\uparrow}},
\]
then by symmetry:
\[
\mathcal{U} \ket{\textcolor{blue}{\uparrow}} = \ket{\textcolor{green}{\uparrow}}, \quad \mathcal{U} \ket{\textcolor{green}{\uparrow}} = \ket{\textcolor{red}{\uparrow}}.
\]
Hence,
\[
\mathcal{U}^3 = \mathds{1}|_{\text{Bloch circle}},
\]
where $\mathds{1}|_{\text{Bloch circle}}$ denotes the identity operator restricted to this subspace. This implies that the ensemble is generated by a cyclic group of order 3, i.e., $\mathbb{Z}/3\mathbb{Z}$.

>>>>

In relation to Postulate I, it is often convenient to represent quantum states using the \emph{density matrix} formalism, where the state is described by $\rho = \ket{\psi}\bra{\psi}$ instead of $\ket{\psi}$. In this formalism, the global phase ambiguity disappears, since if $\ket{\psi'} = e^{i\theta}\ket{\psi}$, then
\begin{align*}
	\rho = \ket{\psi'}\bra{\psi'} = \ket{\psi}\bra{\psi} .
\end{align*}

@@

Note the constraints $\sum_{i=1}^n \Pi_i = \mathds{1}$ and $\Pi_i \geq 0$ ensure that the set $\{\Pi_i\}_{i=1}^n$ form a valid \gls{povm}, since they demand positive semi-definition and form a complete measurement. The superscript $e$ in $P_{\text{\gls{me}}}^e$ indicates that this is the \emph{error probability}.

@@

Naturally, both formulations are related via,
\begin{align*}
P_{\text{\gls{me}}}^s + P_{\text{\gls{me}}}^e = 1.
\end{align*}

In the case of the \gls{ze} protocol, the objective is to exclude with total accuracy a state known to be different from the target state. However, the protocol might lead to inconclusive result. In order to do so, the \gls{povm}s must also satisfy an unambiguity condition, i.e. each measurement operator $\Pi_i$ must be orthogonal to the corresponding state $\rho_i$. In other words,
\begin{align*}
\tr(\Pi_i \rho_i) = 0 \quad \forall i \in \{1, \dots, n\}.
\end{align*}

To ensure completeness, we introduce an additional \gls{povm} element $\Pi_?$ representing an inconclusive result,
\begin{align*}
\Pi_? = \mathds{1} - \sum_{i=1}^n \Pi_i.
\end{align*}
If the measurement yields the outcome $\Pi_?$ (i.e., the "?" symbol), the result is inconclusive.

@@

Let us fix an arbitrary orthonormal basis $\{\ket{\omega_i}\}_{i=1}^n$. Then, the diagonal entries of $X$ in this basis are given by,
\begin{align*}
	X_{i,i} = \braket{\omega_i|\psi_i}.
\end{align*}
\footnote{Note that fixing the basis $\{\ket{\omega_i}\}_{i=1}^n$ uniquely determines the decomposition $\mathcal{G} = X^\dagger X$, and vice versa.}We define the POVM elements as projectors $\Pi_i = \ket{\omega_i}\bra{\omega_i}$. Then, for the ensemble $\{(\rho_i, \eta_i)\}_{i=1}^n$, the corresponding semidefinite program (\gls{sdp}) constrains become,
\begin{align*}
	\tr(\Pi_i \rho_i) &= \tr\left( \ket{\omega_i}\bra{\omega_i} \ket{\psi_i}\bra{\psi_i} \right) \\
	&= |\braket{\omega_i|\psi_i}|^2 \\
	&= |X_{i,i}|^2.
\end{align*}

@@

Given a quantum state $\ket{\psi}$, referred to as the \emph{seed state}, we define a \emph{group generated ensemble} as the set of states obtained by applying a group of unitary transformations to $\ket{\psi}$. Specifically, if the ensemble consists of $n$ quantum states, its elements are of the form,
\begin{align*}
	U_i\ket{\psi}, \quad i \in \{1, \dots, n\},
\end{align*}
where the set of unitary matrices $\{U_i\}_{i=1}^n$ forms a finite group under standard matrix multiplication. In terms of density matrices, the ensemble can equivalently be written as,
\begin{align*}
	\rho_i = U_i \rho U_i^\dagger, \quad i \in \{1, \dots, n\},
\end{align*}
where $\rho = \ket{\psi}\bra{\psi}$ is the density matrix corresponding to the seed state.

@@

\emph{Example: The $\mathbb{Z}/n\mathbb{Z}$ group-generated ensemble}: Let $\mathcal{U} \in U(n)$ be an $n \times n$ unitary matrix satisfying $\mathcal{U}^n = \mathds{1}$, and let $\ket{\psi}$ be the seed state. The Gram matrix $\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}}$ elements associated with the ensemble $\left\{\mathcal{U}^i\ket{\psi}\right\}_{i=0}^{n-1}$ are,
\begin{align*}
	\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}}_{i,j} = \braket{\mathcal{U}^i\psi | \mathcal{U}^j\psi} = \braket{\psi | \mathcal{U}^{j-i} | \psi} = \braket{\mathcal{U}^{j-i}}_{\psi},
\end{align*}
where we use the shorthand notation,
\begin{align*}
	\braket{\mathcal{U}^k}_\psi := \braket{\psi | \mathcal{U}^k | \psi}.
\end{align*}

@@

We now identify $S_3$ as a group of unitary matrices\footnote{We treat each group element as a unitary matrix, and the group operation as matrix multiplication.}. It follows that the Gram matrix of the $S_3$ group-generated ensemble is the matrix of expected values of the Cayley table entries with respect to the seed state $\ket{\psi}$. That is,
\begin{align*}
	\mathcal{G}^{S_3}_{\psi} = \begin{pmatrix}
        1 & \braket{s}_\psi & \braket{s^2}_\psi & \braket{p}_\psi & \braket{q}_\psi & \braket{r}_\psi \\ 
        \braket{s^2}_\psi & 1 & \braket{s}_\psi & \braket{r}_\psi & \braket{p}_\psi & \braket{q}_\psi \\
        \braket{s}_\psi & \braket{s^2}_\psi & 1 & \braket{q}_\psi & \braket{r}_\psi & \braket{p}_\psi \\
        \braket{p}_\psi & \braket{r}_\psi & \braket{q}_\psi & 1 & \braket{s^2}_\psi & \braket{s}_\psi \\
        \braket{q}_\psi & \braket{p}_\psi & \braket{r}_\psi & \braket{s}_\psi & 1 & \braket{s^2}_\psi \\
        \braket{r}_\psi & \braket{q}_\psi & \braket{p}_\psi & \braket{s^2}_\psi & \braket{s}_\psi & 1
	\end{pmatrix}.
\end{align*}
Note that $\braket{e}_\psi = 1$ since $e = \mathds{1}$. Moreover, since $\mathcal{G}^{S_3}$ is Hermitian, we conclude,
\begin{align*}
\braket{p}_{\psi},\ \braket{q}_{\psi},\ \braket{r}_{\psi} \in \mathbb{R}, \quad \forall \ket{\psi} \in \mathcal{H},
\end{align*}
which implies the unitary matrices corresponding to the triangle symmetries $p$, $q$, and $r$ are Hermitian. As a matter of fact we know the eigenvalues of this matrices can only be $\pm 1$ and at least one of them must be $-1$.\footnote{Otherwise, they would be the identity and we know them to be different by construction.} This procedure generalizes to any finite group $G$, showing that computing the Cayley table is equivalent to computing the Gram matrix of the corresponding group-generated ensemble.

Finally, we denote the cardinality of a finite group $G$, i.e. the number of its elements of the group, as $|G|$. In scenarios with uniform prior probabilities, this implies,
\begin{align*}
	\eta_i = \frac{1}{|G|}\quad \forall i\in\{1,...,n\}.
\end{align*}
\subsection{Dual Formulation of the Problem}

@@

Significant progress has been made in the study of the state exclusion task for group-generated ensembles. In particular, the work \emph{Quantum State Exclusion for Group-Generated Ensembles of Pure States}\cite{MainPaper} presents exact analytical expressions for the success and error probabilities under both the Minimum Error (\gls{me}) and Zero Error (\gls{ze}) exclusion protocols.

Let $\mathcal{G}^G$ denote the Gram matrix of a group-generated ensemble $\left\{ \left( \rho_i, \frac{1}{|G|} \right) \right\}_{i=1}^{|G|}$, where $G$ is a finite group of size $|G|$, and let $\{\lambda_i\}_{i=1}^{|G|}$ be the set of eigenvalues of $\mathcal{G}^G$, the Gram Matrix of the group. Assume the eigenvalues are ordered increasingly,
\begin{align*}
	i \leq j \quad \Leftrightarrow \quad \lambda_i \leq \lambda_j, \quad \forall i,j \in \{1, \dots, |G|\},
\end{align*}
i.e., $\lambda_1$ is the smallest and $\lambda_{|G|}$ the largest eigenvalue.

@@

A key feature of these results is their independence from the specific group generating the ensemble. That is, for any two group-generated ensembles $A$ and $B$ corresponding to groups $G_A$ and $G_B$, with $G_A \neq G_B$ but $|G_A| = |G_B|$, if their respective Gram matrices $\mathcal{G}^{G_A}$ and $\mathcal{G}^{G_B}$ share the same eigenvalues, then the exclusion probabilities for both \gls{me} and \gls{ze} protocols are identical. This group-independence property is a cornerstone of the present study.

@@

Let us study the Gram matrix of a limit ensemble composed of $n$ identical quantum states, i.e. the same state is repeated $n$ times in the ensemble.\footnote{This case may appear paradoxical, since there is no way to distinguish between identical states. Nevertheless, we present it as a limiting scenario.} The Gram matrix reads:
\begin{align*}
	\mathcal{G}^{\text{limit}} = \begin{pmatrix}
 1 & 1 & \cdots & 1 \\
 1 & 1 & \cdots & 1 \\
 \vdots & \vdots & \ddots & \vdots \\
 1 & 1 & \cdots & 1 \\
\end{pmatrix}.
\end{align*}

@@

Under these conditions, both \gls{qse} and \gls{qsd} are trivial, as the states form an orthonormal basis. In particular, in the space spanned by these states, we have,
\begin{align*}
	\sum_{i=1}^{n} \rho_i = \mathds{1},
\end{align*}
which means that the set $\{\rho_i\}$ is itself a \gls{povm}. The measurement corresponding to this \gls{povm} allows perfect identification, or exclusion, hence both \gls{qse} and \gls{qsd} can be performed without error.

@@

In the non-perfect exclusion regime, the analytical results for group-generated ensembles provide lower bounds on the success probabilities, and upper bounds on the error probabilities for general ensembles.

Consider, for example, the case of an ensemble of 4 quantum states. There are exactly two groups of four elements, $\mathbb{Z}/4\mathbb{Z}$ and $\mathbb{Z}/2\mathbb{Z} \times \mathbb{Z}/2\mathbb{Z}$.\footnote{These are the only non-isomorphic groups of order 4.} This implies that there exist two specific unitary matrices, $U_{\mathbb{Z}/4\mathbb{Z}}$ and $U_{\mathbb{Z}/2\mathbb{Z} \times \mathbb{Z}/2\mathbb{Z}}$ (up to permutation of rows and columns), for which the analytical solution holds exactly.

Since $U(n)$ is compact, and assuming continuity of the exclusion probabilities with respect to $U$ under a given matrix norm, for each of these unitary matrices there exist arbitrarily small neighborhoods $\mathcal{B}(U_{\mathbb{Z}/4\mathbb{Z}})$ and $\mathcal{B}(U_{\mathbb{Z}/2\mathbb{Z} \times \mathbb{Z}/2\mathbb{Z}})$ such that the exclusion probabilities within these neighborhoods approximate the analytical result as closely as desired. However, the existence of multiple such matrices, and intersecting neighborhoods, can complicate numerical optimization and analysis.

In contrast, it is usefull to consider the case where the ensemble contains a prime number $p$ of states. In this scenario, the situation simplifies considerably, since there exists only one group, up to isomorphism, of order $p$, namely $\mathbb{Z}/p\mathbb{Z}$.

This result follows immediately from Lagrange's theorem. The theorem guarantees the order of any element in a finite group\footnote{The order of an element $\tau$ in a group $G$ is the smallest positive integer $m$ such that $\tau^m = e$, where $e$ denotes the identity/neutral element of the group.} must divide the order of the group. Since $p$ is a prime number, the only positive integers dividing $p$ are either $1$ or $p$ itself. Therefore, the order of any group element must be either $1$ or $p$. An element of order $1$ must be the identity, so every non-identity element in the group must have order $p$. This implies that all non-identity elements generate the entire group, i.e., the group is cyclic. As a result, any group of prime order $p$ is necessarily cyclic and isomorphic to $\mathbb{Z}/p\mathbb{Z}$.

@@

Ensembles of prime cardinality are thus of particular interest and will be further explored in the Results and Discussion (section \ref{sectionResultsAndDiscussion}).

\section{Methodology}

@@

\section{Results and Discussion}\label{sectionResultsAndDiscussion}

@@

The colorless regions correspond to parameters where $\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}$ is not positive semi-definite, and leading up to non-valid Gram matrices, since positive semi-definition is inherent to a Gram matrix.

@@

Both limiting behaviors remain valid. However, the \gls{ze} success probabilities are lower than those of the \gls{me} protocol. This is explained by the stricter constraints imposed in the \gls{ze} scenario, where $\tr(\Pi_i\rho_i) = 0$ is enforced for all \gls{povm} elements except one. Notice both probabilities are computed in a completely symmetric way,
\begin{align*}
	P^s_{\gls{me}}\sim P^s_{\gls{ze}}\sim 1-\sum_{\gls{povm}}\tr{(\Pi_i\rho_i)}.
\end{align*}

Nevertheless, in the \gls{ze} case we enforce $\tr{(\Pi_i\rho_i)}=0$ for all the \glspl{povm} except one\footnote{Naturally the \gls{povm} that is not enforced to be orthogonal is the one that yields to an inconclusive result, i.e. $\Pi_?$.}. Thus, the system is more constrained in the \gls{ze} protocol, then the optimization of the probability cannot be performed up to the same point as in the \gls{me} protocol. Hence, the success probabilities for \gls{me} are greater than the ones obtained with the \gls{ze} protocol.

@@

Notice the missing eigenvalue is determined by the other two via,
\begin{align*}
	\lambda_3=3-\lambda_1-\lambda_2.
\end{align*}
Since the Gram matrix is a positive semidefinite matrix we know that $\lambda_3\geq0$, the limit case scenario $\lambda_3=0$ defines the line,
\begin{align*}
\lambda_2=3-\lambda_1,
\end{align*}
that constraints the possible eigenvalues to only reach values under this line. Otherwise the remaining value would be negative leading up to non-valid Gram matrices as discussed in the previos plots. Naturally, we also know $\lambda_1,\lambda_2>0$, then the region $\Omega$ where the system leads up to consistent Gram matrices is,
\begin{align*}
	\Omega=\left\{(\lambda_1,\lambda_2)\in\mathbb{R}^2\left|\lambda_1\geq0,\lambda_2\geq0,\lambda_1+\lambda_2\leq3\right.\right\}.
\end{align*}
This region $\Omega$ is depicted in the Figure (\ref{FigureQSEMEZ3ZEigenValues}) as boottom left triangle, where our system is recluded. Inside this region we can find the perfect exclusion zone, i.e. the eigenvalues such that Eq.(\ref{equationPerfectExclusionCondition}) is fulfilled. In particular, if we set $\lambda_i$ with $i\in\{1,2,3\}$ to be the greatest eigenvalues and denote $\lambda_j,\lambda_k$ as the remaining 2 eigenvalues, we know perfect exclusion to be archived if,
\begin{align*}
	\sqrt{\lambda_i}\leq \sqrt{\lambda_j}+\sqrt{\lambda_k}.
\end{align*}
With a little bit of algebra and recalling that $\lambda_3=3-\lambda_1-\lambda_2$ we can derive the regime of perfect exclusion denoted as $\Delta$ comprehends the eigenvalues such that,
\begin{align*}
	(\lambda_1,\lambda_2&)\in \Delta\\
	\Updownarrow& \\
	4\lambda_1^2 + 4\lambda_2^2 + 4\lambda_1\lambda_2 - &12\lambda_1 - 12\lambda_2 + 9 \leq 0
\end{align*}
Figure (\ref{FigurePerfectExclusionZ3Z}) shows the $\Delta$ region. It is inmediate that this region corresponds to the colorless perfect exclusion regime in Figure (\ref{FigureQSEMEZ3ZEigenValues}).
\begin{figure}[H]
	\centering
	\begin{overpic}[width=0.5\textwidth, trim={1.8cm 0.8cm 2cm 2cm}, clip]{GeneralSources/PerfectExclusionZoneZ3Z.pdf}
	\end{overpic}
	\caption{Plot of the $\Delta$ region.}
	\label{FigurePerfectExclusionZ3Z}
\end{figure}

@@

To illustrate this more concretely, consider the following ensamble involving qubit states,
\[
\{\ket{\textcolor{red}{\uparrow}}, \ket{\textcolor{blue}{\uparrow}}, \ket{\textcolor{green}{\uparrow}}\}.
\]
These are represented on a Bloch circle\footnote{The Bloch circle is a projection of the Bloch sphere onto a plane.} in Figure (\ref{FigureIntuitionExample}).

@@

It is evident that $\ket{\textcolor{red}{\uparrow}}$ is noticeably different from the other two states. The red arrow points in the opposite direction to the blue and green arrows. Therefore, given an unknown state $\ket{\uparrow}$ from this ensemble, it is relatively easy to determine whether $\ket{\uparrow} = \ket{\textcolor{red}{\uparrow}}$ or $\ket{\uparrow} \neq \ket{\textcolor{red}{\uparrow}}$. If $\ket{\uparrow} = \ket{\textcolor{red}{\uparrow}}$, we can exclude either $\ket{\textcolor{blue}{\uparrow}}$ or $\ket{\textcolor{green}{\uparrow}}$, otherwise, we can exclude $\ket{\textcolor{red}{\uparrow}}$. In both cases, the exclusion is straightforward.

@@

This configuration exhibits perfect symmetry. Define a unitary operator $\mathcal{U}$ such that,
\begin{align*}
\mathcal{U} \ket{\textcolor{red}{\uparrow}} = \ket{\textcolor{blue}{\uparrow}},
\end{align*}
then by symmetry,
\begin{align*}
\mathcal{U} \ket{\textcolor{blue}{\uparrow}} = \ket{\textcolor{green}{\uparrow}}, \quad \mathcal{U} \ket{\textcolor{green}{\uparrow}} = \ket{\textcolor{red}{\uparrow}}.
\end{align*}
Hence,
\begin{align*}
\mathcal{U}^3 = \mathds{1}|_{\text{Bloch circle}},
\end{align*}
where $\mathds{1}|_{\text{Bloch circle}}$ denotes the identity operator restricted to this subspace. This implies the ensemble is generated by a cyclic group of order 3, i.e., $\mathbb{Z}/3\mathbb{Z}$.
